Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Update todo
Update online sources

% After wednesday meeting with Chris
% TODO: Algorithm showing the edge projected distance algorithm for the collision study
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Spell check
% TODO: Go over report one final time

@@

\bibitem{lantmateriet-19}
(Lantmäteriet, 2019), Produktbeskrivning: GSD-Fastighetskartan vektor \\ 
\href{https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf}.

\bibitem{osm-19}
(OSM 19) Converting to WGS84, accessed 13-03-2020 \\ 
\href{https://wiki.openstreetmap.org/wiki/Converting\_to\_WGS84}.

\bibitem{osm-20}
(OSM 20) OSM History Viewer\\
\href{https://wiki.openstreetmap.org/wiki/OSM\_History\_Viewer}.

>>>>

% After wednesday meeting with Chris
% TODO: Algorithm showing the edge projected distance algorithm for the collision study
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Fix citations so they adhere to the same model
% TODO: Spell check
% TODO: Go over report one final time

@@

\bibitem{lantmateriet-19}
Lantmäteriet. (2019). Produktbeskrivning: GSD-Fastighetskartan vektor. Acessed 16-04-2020. \\ 
https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf.

\bibitem{osm-19}
OSM. (2019). Converting to WGS84 - OpenStreetMap Wiki. Accessed 13-03-2020. \\ 
https://wiki.openstreetmap.org/wiki/Converting\_to\_WGS84.

\bibitem{osm-20}
(OSM 20) OSM History Viewer - OpenStreetMap Wiki. Accessed 20-03-2020. \\
https://wiki.openstreetmap.org/wiki/OSM\_History\_Viewer.
